### 2021-08-10 paper/paper.tex
Replace "ca." by approximately and remove it where already a range is given

The most important design decision was to create \trixi as a library. In the
context of simulation-focused scientific computing, there are many (open
or closed source) codes that are designed as monolithic applications that can
simulate a specific setup. These codes can often be configured to a limited extent
by specifying compile time options or editing parameter files. In contrast, users of
\trixi do not need to compile anything or learn parameter file syntax. Instead, they can
just load the library and write their simulation setups in Julia. Scripts that describe
a simulation setup for \trixi are referred to as ``elixirs''. As of version
v0.3.55 (August 2021), \trixi comes with \ca 200 example elixirs. A basic elixir
might look as follows:

@@

Finally, the different mesh types available in \trixi allow further optimizations.
For example, if the computational domain is essentially a cube (or square, line)
without need for curvilinear coordinates, the Cartesian \lstinline{TreeMesh} can
be used. Depending on the relative computational effort of the discretization
(such as the polynomial degree and the choice of the volume terms), the
Cartesian \lstinline{TreeMesh} can be \ca \SI{10}{\percent} to \SI{25}{\percent}
more efficient than the curvilinear meshes in \trixi.

>>>>

The most important design decision was to create \trixi as a library. In the
context of simulation-focused scientific computing, there are many (open
or closed source) codes that are designed as monolithic applications that can
simulate a specific setup. These codes can often be configured to a limited extent
by specifying compile time options or editing parameter files. In contrast, users of
\trixi do not need to compile anything or learn parameter file syntax. Instead, they can
just load the library and write their simulation setups in Julia. Scripts that describe
a simulation setup for \trixi are referred to as ``elixirs''. As of version
v0.3.55 (August 2021), \trixi comes with approximately 200 example elixirs. A basic elixir
might look as follows:

@@

Finally, the different mesh types available in \trixi allow further optimizations.
For example, if the computational domain is essentially a cube (or square, line)
without need for curvilinear coordinates, the Cartesian \lstinline{TreeMesh} can
be used. Depending on the relative computational effort of the discretization
(such as the polynomial degree and the choice of the volume terms), the
Cartesian \lstinline{TreeMesh} can be \SI{10}{\percent} to \SI{25}{\percent}
more efficient than the curvilinear meshes in \trixi.
